Flabby and injective objects in toposes

### 2022-02-14 paper-flabby-objects.tex
to do
typo

\begin{proof}[Proof of Proposition~\ref{prop:flabby-effective-sets}]
Let~$X$ be an object of the \effective topos. Then the object~$P_{\leq1}(X)$ of
subterminals of~$X$ is a uniform object in the sense
of~\cite[Section~3.4]{moerdijk-oosten:topos-theory}, being a retract of the
uniform object~$P(X)$ by the surjection
\[ P(X) \longrightarrow P_{\leq1}(X),\
  M \longmapsto \{ x \in X \,|\, M = \{ x \} \}. \]
Hence if~$X$ is \effective, the uniformity principle~\cite[Proposition~15.1]{hyland:effective-topos}
\[ \forall K \in P_{\leq1}(X)\_
  \exists x \in X\_ K \subseteq \{x\} \quad\Longrightarrow\quad
  \exists x_0 \in X\_ \forall K \in P_{\leq1}(X)\_ K \subseteq \{x_0\} \]
applies. Thus, if~$X$ is \effective and flabby, there is
an element~$x_0 \in X$ such that~$K \subseteq \{x_0\}$ for any subterminal~$K$
of~$X$. The conclusion follows by considering, for any elements~$a,b \in X$,
the subterminals~$\{a\}$ and~$\{b\}$.
\end{proof}

@@

>>>>

\begin{proof}[Proof of Proposition~\ref{prop:flabby-effective-sets}]
Let~$X$ be an object of the \effective topos. Then the object~$P_{\leq1}(X)$ of
subterminals of~$X$ is a uniform object in the sense
of~\cite[Section~3.4]{moerdijk-oosten:topos-theory}, being a retract of the
uniform object~$\P(X)$ by the surjection
\[ \P(X) \longrightarrow \P_{\leq1}(X),\
  M \longmapsto \{ x \in X \,|\, M = \{ x \} \}. \]
Hence if~$X$ is \effective, the uniformity principle~\cite[Proposition~15.1]{hyland:effective-topos}
\[ \forall K \in \P_{\leq1}(X)\_
  \exists x \in X\_ K \subseteq \{x\} \quad\Longrightarrow\quad
  \exists x_0 \in X\_ \forall K \in \P_{\leq1}(X)\_ K \subseteq \{x_0\} \]
applies. Thus, if~$X$ is \effective and flabby, there is
an element~$x_0 \in X$ such that~$K \subseteq \{x_0\}$ for any subterminal~$K$
of~$X$. The conclusion follows by considering, for any elements~$a,b \in X$,
the subterminals~$\{a\}$ and~$\{b\}$.
\end{proof}

@@

Cite! https://arxiv.org/pdf/2008.10677.pdf
